---
title: "Publications"
description: |
  My recent publications and conference presentations. 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r write_refs, include = FALSE, cache = FALSE}
library(RefManageR)
# Grab bibTeX using DOIs, and save to pubs.bib
RefManageR::GetBibEntryWithDOI(
  unique(
    c("10.1080/10705511.2021.1977936",
      "10.1037/met0000455")
  ), 
  temp.file = "pubs.bib", 
  delete.file = FALSE)
# Manual bibTeX for articles withoutin DOIs
ref <- c(
  BibEntry(
    bibtype = "unpublished", 
    key = "Lai2021b", 
    title = "Adjusting for measurement error in cluster means in multilevel modeling: Two numerically stable alternatives to latent-mean centering.", 
    author = "Lai, Mark H. C. and Zhang, Yichi and Feng, Ji", 
    year = "2021", 
    pubstate = "Under review"
  ),
  BibEntry(
    bibtype = "unpublished", 
    key = "Tse2021", 
    title = "Does strict invariance matter? valid group mean comparisons with ordered-categorical items",
    author = "Tse, Winnie Wing-Yee and Lai, Mark H. C. and Zhang, Yichi", 
    year = "2022", 
    pubstate = "In progress"
  ),
  BibEntry(
    bibtype = "unpublished", 
    key = "Zhang2021", 
    title = "Evaluating Standard Error Estimators for Multilevel Models on Small Samples With Heteroscedasticity and Unbalanced Cluster Sizes",
    author = "Zhang, Yichi and Lai, Mark H. C.", 
    year = "2022", 
    pubstate = "In progress"
  )
)
WriteBib(bib = ref, 
         file = "pubs.bib", 
         append = TRUE)
```

```{r, load_refs, include = FALSE, cache = FALSE}
library(RefManageR)
# Grab bibTeX using DOIs, and save to pubs.bib
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE, 
           no.print.fields = "url")
myBib <- ReadBib(here::here("pubs.bib"), check = FALSE)
```

## Peer-Reviewed Articles (Selected)

### 2022

```{r, results = "asis"}
myBib[date = "2022"]
```

### 2021

```{r, results = "asis"}
myBib[date = "2021"]
```

## Conference Presentations

### 2022

- Zhang, Y. Lai, M. H. C. (2022, July 11-15). *Bayesian Region of Measurement Equivalence Approach with Alignment* [Oral Presentation]. Annual Meeting of the Psychometric Society (IMPS), Bologna, Italy.

- Zhang, Y. Lai, M. H. C. (2022, July 11-15). *Inferences with Multilevel Model: What if You have Small, Unbalanced, Heteroscedastic Samples?* [Poster Presentation]. Annual Meeting of the Psychometric Society (IMPS), Bologna, Italy.

- Zhang, Y. Lai, M. H. C. (2022, April 21-26). *Evaluating Standard Error Estimators for Multilevel Models on Small Samples With Heteroscedasticity and Unbalanced Cluster Sizes.* American Educational Research Association Annual Meeting, San Diego, Ca, United States.

### 2021

- Zhang, Y. & Lai, M. H. C. (2021, August 12-14). *Classification accuracy of multidimensional tests: Quantifying the impact of noninvariance* [Poster Session]. American Psychological Association Annual Convention (APA), Online.
- Zhang, Y. & Lai, M. H. C. (2021, July 20-23). *Classification accuracy of multidimensional tests: Quantifying the impact of noninvariance* [Oral Presentation]. Annual Meeting of the Psychometric Society (IMPS), College Park, MD, United States.
- Zhang, R., Zhang, Y., & Lalonde, R. (2021, July 27-31). *Examining multiculturalism-creativity link from the perspective of challenge and threat appraisals* [Oral Presentation]. International Association of Cross-Cultural Psychology (IACCP), online.

### 2020

- Zhang, Y. & Lai, M. H. C. (2020, July 14-17). *A Bayesian Region of Measurement Equivalence (ROME) Approach for Establishing Measurement Invariance* [Poster Session]. Annual Meeting of the Psychometric Society (IMPS), College Park, MD, United States. [Schedule](https://www.psychometricsociety.org/sites/main/files/file-attachments/imps_2020_virtual_schedule_g1.pdf?1594692842)
- Zhang, Y. & Lai, M. H. C. (2020, June 2-3). *A Bayesian Region of Measurement Equivalence (ROME) Approach for Establishing Measurement Invariance* [Poster Session]. Modern Modeling Methods Conference (MMM), Storrs, CT, United States. (Conference canceled)
